### 2023-06-29 2023/certificates/gen_certificates_ornament.tex
certificates remove solver without members, experimental divisions
remove experimental logic

\documentclass[a4paper,landscape,12pt]{article}
\usepackage[svgnames]{xcolor}
\usepackage{wallpaper}
\usepackage{ragged2e}
\usepackage{ulem}
\usepackage{etoolbox}
\usepackage[object=pgfhan]{pgfornament}
\usetikzlibrary{chains}
\usetikzlibrary{calc}
\usetikzlibrary{decorations}
\usetikzlibrary{decorations.text,decorations.markings}
\usetikzlibrary {decorations.pathmorphing,shadows}

\usepackage{geometry}
\geometry{hmargin=1in,vmargin=0.8in,headheight=10pt}

@@

\newcommand{\seq}{\texttt{;}}
\newcommand{\paral}{\textbardbl}
\newcommand{\sat}{$\top$}
\newcommand{\unsat}{$\bot$}
\newcommand{\fast}{\texttt{24}}
\newcommand{\inc}{inc}
\newcommand{\uc}{uc\textsuperscript}
\newcommand{\mv}{mv\textsuperscript}
\newcommand{\cloud}{cloud}
\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
\newcommand{\withtrack}[2]{\textsc{#1}{{\footnotesize (#2)}}}

@@

    \medskip
    \ifstrempty{#2}{}{
    \textcolor{red!30!black!90}
    {\textit{Certificate for overall performance}}

@@

    \ifstrempty{#3}{}{
    \textcolor{red!30!black!90} {\textit{Certificate for divisions}}

@@

    \ifstrempty{#4}{}{
     \textcolor{red!30!black!90}  {\textit{Certificate for logic}}

@@

    {\color{blue!40!black}
    \scalebox{.7}{
    \begin{tabular}{ccccc}
    \cline{1-1} 
    \cline{3-3}
    \cline{5-5}
    \\ \
    Jochen Hoenicke  & &  Bobot François & & Martin Bromberger \\
    Organizer & & Chair & & Organizer \\ 
    \end{tabular}
    }}
    \end{myframe}

>>>>

\documentclass[a4paper,landscape,12pt]{article}
\usepackage[svgnames]{xcolor}
\usepackage{wallpaper}
\usepackage{ragged2e}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{etoolbox}
\usepackage[object=pgfhan]{pgfornament}
\usetikzlibrary{chains}
\usetikzlibrary{calc}
\usetikzlibrary{decorations}
\usetikzlibrary{decorations.text,decorations.markings}
\usetikzlibrary{decorations.pathmorphing,shadows}

\usepackage{geometry}
\geometry{hmargin=1in,vmargin=0.8in,headheight=25pt}

@@

\newcommand{\seq}{\texttt{;}}
\newcommand{\paral}{\textbardbl}
\newcommand{\sat}{$\top$}
\newcommand{\unsat}{$\bot$}
\newcommand{\fast}{\texttt{24}}
\newcommand{\inc}{inc}
\newcommand{\uc}{uc}
\newcommand{\mv}{mv}
\newcommand{\cloud}{cloud}
\newcommand{\paralTrack}{parallel}
%\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
\newcommand{\withtrack}[2]{\textsc{#1}{{\footnotesize (#2)}}}

@@

    \medskip
    \ifstrempty{#2}{}{
    \textcolor{red!30!black!90}
    {\textit{Solver won overall}}

@@

    \ifstrempty{#3}{}{
    \textcolor{red!30!black!90} {\textit{Solver won division}}

@@

    \ifstrempty{#4}{}{
     \textcolor{red!30!black!90}  {\textit{Solver won logic \ifstrempty{#3}{}{(but not the corresponding division)}}}

@@

    {\color{blue!40!black}
%    \scalebox{.7}{
    {\tiny
    \begin{tabular}{ccccc}
        \includegraphics[scale=0.5]{signature-blank-crop-jochen.pdf} && && \includegraphics{MB-Signature.png} \\
    \cline{1-1} 
    \cline{3-3}
    \cline{5-5}
    \\ \
    Jochen Hoenicke  & &  Bobot François & & Martin Bromberger \\
    Organizer & & Chair & & Organizer \\ 
    \end{tabular}
    }}
    \end{myframe}

### 2023-06-29 2023/certificates/input_for_certificates.tex
remove experimental logic

\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}}

@@

\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{ALIA}{\sat,\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{UFLIA}{\sat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{UFIDL}{\sat}, \withtrack{AUFDTLIA}{\uc}}

@@

\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{Bitvec}{\sat}}{\withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{ABVFP}{\sat,\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{ABVFPLRA}{\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}}

@@

\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{AUFLIRA}{\fast}}

@@

\MakeOnePage{Yices2}{}{\withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}, \withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}}{\withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}}

@@

\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_LinearRealArith}{\unsat}}{\withtrack{QF\_FP}{\sat,\mv}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{LIA}{\sat,\fast}, \withtrack{UFDT}{\fast}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_AUFLIA}{\uc,\mv}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_AX}{\mv}}

@@

\MakeOnePage{OpenSMT}{}{\withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}, \withtrack{QF\_Equality+LinearArith}{\unsat}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}

>>>>

\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}}

@@

\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}

@@

\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}

@@

\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}

@@

\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc}}

@@

\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}

@@

\MakeOnePage{OpenSMT}{}{\withtrack{QF\_Equality+LinearArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}
